Considering scale in multilayer animal social networks

### 2020-06-16 paper/manuscript.Rmd
question 35-36 days

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social association between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36
days taken from the entire study period. Social associations were defined by
spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
window, we calculated individual graph strength and multidegree, and across the
series of networks, we calculated edge overlap to determine proportion of total
edges observed in each time window.

>>>>

### Temporal scale
#### Time windows 
We used a temporal multilayer network to assess the seasonality of caribou
sociality. Multilayer networks consisted of the social association between 
`r DT[, uniqueN(get(idcol))]` individuals across 20 ordinal sample periods of 35-36 <!--QW: why 35-36 and not just 35 or 36?-->
days taken from the entire study period. Social associations were defined by
spatiotemporal overlap of individuals within 5 minutes and 50 m. In each time
window, we calculated individual graph strength and multidegree, and across the
series of networks, we calculated edge overlap to determine proportion of total
edges observed in each time window.
